Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-10-03 tex/sup/supplementary_information.tex
update introduction of sup text

%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
\SItext{This supplementary document consists of three sections and 10 figures. Firstly, we introduced our study area, the Yellow River Basin, in the section Methods S1. Definition of study area. Then, we give a detailed description of used datasets and analysis their uncertainties in the section Methods S2. Detailed information on dataset and processing. Finally, the index along with corresponding indicators are introduced in the section Methods S3. Water Utility Regime Index.}

@@

% 补充图片3：天然水资源量
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
    \caption{Water resources in different regions. 
        \textbf{A,} changing trend of measured runoff, 
        \textbf{B, C and D} average measured runoff within different periods.
        \textbf{E, F and G} average total water consumptions within different periods. 
    }
\end{figure}

>>>>

%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
\SItext{This supplementary document consists of four \textit{Methods} sections, 9 \textit{SI Appendix} figures and 2 \textit{SI Appendix} tables. Firstly, we introduced our study area, the Yellow River Basin, and its subdivisions in the section Methods S1. Then, we give a detailed description of used datasets and analysis their uncertainties in the section Methods S2. Further, we introduced how to harmonized different datasets with various spatial and temporal scales in Methods S3. Finally, the index along with corresponding indicators are introduced in the section Methods S4.}

@@

% 补充图片3：天然水资源量
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
    \caption{Water resources in different regions. 
        \textbf{A,} changing trend of measured runoff, 
        \textbf{B, C and D} average measured runoff within different periods.
        \textbf{E, F and G} average total water consumptions within different periods. 
    }
\end{figure}
